\chapter{Technologies used}

\section{MySQL}

\textit{MySQL} is an open-source database management system, we can manage the database with the SQL langage.  It has been founded in 1995 and it is one of the most used database system in the world.

\section{JAVA}
\subsection{Tomcat}

Tomcat is an open source web server that provide an environment to run \textit{JAVA} and \textit{J2EE} code.

\subsection{Spring}
\textit{Spring} is a \textit{JAVA} framework which allows to build simple and complex applications easily. From web applications to big data, \textit{Spring} is really modular. Since 2002, the framework is used worldwide by a lot of companies. 


\subsection{Hibernate}
Hibernate is an \textit{Object Relation Mapper}. It provides a lot of simplification for the database management. For Hibernate, all database data is object. With the help of annotations provided by \textit{JAVA}, you can specify the relationships between all objects (Many-To-Many, Many-To-One, etc...) 


\subsection{Pebble}
Derived from the powerful template engine written en \textit{PHP}, \textit{Twig}, Pebble is a library which allows to create views for the MVC model. Because it has a Spring implementation, we could use it inside this project. This template engine is easy to learn and master. It have been thought for designers and have a really friendly syntax.

\section{HTML5/CSS3}

HTML5 and CSS3 are two langage that allow to create static web page.
HTML5 is done to manage the structure of the page (title, section...) and CSS3 can manage the design of the website (size, image, color...)


\section{NodeJS}



\section{Asterisk}



\section{Git}

Git is a version control system, it is widely used by developper to prevent loss of code and help in the organisation and communication in a project


\section{Maven}

Maven is a build automation tool used primarily for Java projects, it ease the management of the dependency between every technologies in the project.


\newpage